%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

\hypersetup{%
  colorlinks=true,% hyperlinks will be coloured
}

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Kartik Behl} \\ \vspace{1pt}
    \small \href{tel:9990290880}{+91-9990290880} $|$ \href{mailto:kartikbehl.p99@gmail.com}{\underline{kartikbehl.p99@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/kartik-b-b46a3484/}{\underline{LinkedIn}} $|$
    \href{https://github.com/kartikbehl99}{\underline{GitHub}}
\end{center}


%-----------SUMMARY-----------
\section{Summary}
\resumeSubHeadingListStart
\resumeItem{A creative and detailed individual with ability to develop effective and efficient solutions with zero tolerance for errors. Looking forward to fully harness my technical skills.}
\resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Maharaja Agrasen Institute of Technology}{Delhi, India}
      {Bachelor of Technology, Information Technology, CGPA: 8.7/10.0}{2017 - 2021}
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, JavaScript, Ruby, SQL, HTML, CSS} \\
     \textbf{Frameworks}{: Flask, Angular, Ruby on Rails} \\
     \textbf{Database}{: PostgreSQL, MySQL, DynamoDB, MongoDB} \\
     \textbf{Tools and Technologies}{: Git, AWS, Selenium, Ansible, Docker, Celery, RabbitMQ} \\
     \textbf{Other Skills}{: Data Structures, Algorithms, OO Design, System Design, Cloud Computing} \\
    }}
 \end{itemize}
%-------------------------------------------


%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{July 2020 -- Present}
      {Coding Ninjas}{}
      \resumeItemListStart
        \resumeItem{Work as a full-stack developer and develop end-to-end features using Angular and Rails.}
        \resumeItem{Develop sophisticated \href{https://www.codingninjas.com/courses/premium-foundation-course}{web pages} and create APIs for the same.}
        \resumeItem{Significantly reduced API response time by caching the results and optimizing database queries.}
        \resumeItem{Developed and own the system for automating the process of certificate generation and distribution.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Software Engineer}{June 2019 -- June 2020}
      {OpsLyft}{}
      \resumeItemListStart
        \resumeItem{Conceived and built the first version of the product, used CUR reports with AWS Athena to provide customised dashboards to our customers with 1-click integration via CFN templates.}
        \resumeItem{Developed the backend of the product from scratch and achieved the MVP state in a span of 3 months.}
        \resumeItem{Built features like rightsizing, Idle resources monitoring into the product.}
        \resumeItem{Developed marketing tech products which added automation in sales and lead generation.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{SSH Manager} $|$ \emph{Flask, AWS EC2, DynamoDB, SSH, Ansible}}{\href{https://github.com/kartikbehl99/ssh-manager-backend}{Code}}
          \resumeItemListStart
            \resumeItem{A CLI tool for managing SSH keys of an organization and SSH to the server.}
            \resumeItem{Encrypts all the keys with a password known to the user only and isn’t stored any where else.}
            \resumeItem{Allows controlling who has access to a particular SSH key.(This project isn't deployed anywhere because it requires a dedicated infrastructure on cloud)}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Code Runner as a Service} $|$ \emph{Flask, Docker, Shell, RabbitMQ, Celery, Nginx, Gunicorn, AWS EC2}}{\href{https://github.com/thephilomaths/code-runner-as-a-service}{Code} $|$ \href{https://www.postman.com/kartikbehl99/workspace/code-runner-workspace/overview}{Demo}}
          \resumeItemListStart
            \resumeItem{It a Saas project which runs C++/Java/Python codes in a completely sandboxed environment.}
            \resumeItem{It supports both synchronous and asynchronous execution of code.}
         \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{URL Shortener} $|$ \emph{Angular, Flask, Nginx, MongoDB, EC2}}{\href{https://github.com/kartikbehl99/URL-shortener-public}{Code} $|$ \href{https://smol.ga}{Demo}}
          \resumeItemListStart
            \resumeItem{A URL shortener capable of generating ~3 trillion unique URLs without the need of checking for collisions.}
          \resumeItem{Implemented IP based rate limiting(1 second/request) to prevent exploitation of resources.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Automated user behaviour mapping} $|$ \emph{Python, SocketIO, JavaScript, Selenium}}{\href{https://github.com/kartikbehl99/automated-user-behaviour-mapping}{Code}}
          \resumeItemListStart
            \resumeItem{A javascript and python based app which records all the actions performed by a user on a website in real-time.}
            \resumeItem{It then shows how the user operated the website/webpage by replicating the actions in a browser window.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{AWS Cost Dashboard $|$ Developed at OpsLyft}}{\href{https://grafana.opslyft.com}{Demo (Contact me for credentials)}}
          \resumeItemListStart
            \resumeItem{It is aimed at providing near real-time cost analytics and usage of various AWS services thereby providing 100\% visibility of cloud infrastructure}
            \resumeItem{It also gives real-time insights about usage statistics such as CPU Utilization, Memory Utilization, Volume used etc which helps in granular level management of resources and saves 1000s of dollars.}
         \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}
