%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% CV Bruno Alves 06/2017 %%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper]{main}

%Layout
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm,footskip=2\baselineskip}

%Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage{hyperref}

%Colors

\definecolor{accent}{HTML}{000e17}
\definecolor{heading}{HTML}{000e17}
\definecolor{emphasis}{HTML}{696969}
\definecolor{body}{HTML}{01415f}

\colorlet{heading}{heading}
\colorlet{accent}{accent}
\colorlet{emphasis}{emphasis}
\colorlet{body}{body}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%

\begin{document}
\name{Kartik Behl}
\tagline{}
\personalinfo{
  \email{\href{mailto:kartikbehl99@gmail.com}{kartikbehl99@gmail.com}}
  \phone{\href{tel:9990290880}{+91 9990290880}}
  \linkedin{\href{https://www.linkedin.com/in/kartik-behl-b46a3484/}{kartikbehl99}}
  \github{\href{https:github.com/kartikbehl99}{kartikbehl99}}
}

%

\begin{fullwidth}
\makecvheader
\end{fullwidth}

%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Experience %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection[page1sidebar]{Experience}

%%%%%%%%%%%%%
%Experience 1
%%%%%%%%%%%%%

\cvevent{Software Engineer Intern}{Coding Ninjas}{July 2020 -- Present}{New Delhi, India}

\begin{itemize}
	\item Working as a full stack developer, using Ruby on Rails and Angular for development.
    \item Develop End-to-End features for the product.
    \item Fixing bugs in production.
\end{itemize}

\divider
%

%%%%%%%%%%%%%
%Experience 2
%%%%%%%%%%%%%

\cvevent{Software Engineern Intern}{OpsLyft}{June 2019 -- June 2020}{Noida, India}

\begin{itemize}
  \item Developed and optimized the backend of the product.
    \item Automated deployment process using ansible.
    \item Designed scalable architecture on AWS and worked with various AWS services.
    \item Developed tech products for marketing team such as Sales navigator scraper, Crunchbase scraper and Bulk email sender.
\end{itemize}

\divider
%

%%%%%%%%%%%%%
%Experience 3
%%%%%%%%%%%%%

\cvevent{Teaching Assistant}{Coding Ninjas}{January 2018 -- April 2018}{New Delhi, India}

\begin{itemize}
  \item Worked as a TA for Data structures and Algorithms.
\end{itemize}

\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Projects}

%%%%%%%%%%%%%
%Project 1
%%%%%%%%%%%%%

\cveventproject{SSH Key Manager}{Personal Project}{April 2020 -- Present}

\begin{itemize}
    \item It is a CLI tool for managing SSH keys of an organization and SSH to the server. It encrypts all the keys with a password known to the user only and isn't stored any where else. The tool also allows controlling who has access to a particular SSH key.
    \item Technologies: Flask, AWS EC2, AWS DynamoDB, SSH, Ansible.
\end{itemize}

\divider

%

%%%%%%%%%%%%%
%Project 2
%%%%%%%%%%%%%

\cveventproject{AWS Cost Dashboard}{Developed at OpsLyft}{March 2020 -- June 2020}

\begin{itemize}
    \item AWS Cost Dashboard is aimed at providing near real time cost analytics and usage of various AWS services namely ECS, EC2, RDS, Lambda, S3, Dynamodb.
    \item It also shows various real time usage statistics such as CPU Utilisation, Memory Utilisation, Volume used etc.
    \item Technologies: Python, Flask, ReactJs, AWS(EC2, Redshift, S3, Lambda, CloudFormation etc.), boto3.
\end{itemize}

%

\end{document}
